Automated Verification of Stand-Alone Solar Photovoltaic Systems

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

\includegraphics[width=0.4\textwidth]{flowchart_verification4.png}

@@

\caption{Flowchart of the proposed automated verification of PV systems. \textcolor{red}{replace ``show fail detail'' by ``show counterexample''. replace ``non deterministic test of variables'' by ``non-deterministic variables''. replace ``Project OK'' by ``Project meets the specification up to the given bound''.}}

>>>>

\includegraphics[width=0.4\textwidth]{flowchart_verification5.png}

@@

\caption{Flowchart of the proposed automated verification of PV systems.}
